%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

%\RequirePackage{bibentry}
%\makeatletter\let\saved@bibitem\@bibitem\makeatother

\documentclass[10pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

%\makeatletter\let\@bibitem\saved@bibitem\makeatother


% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
%\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
%\usepackage{notoccite}
\usepackage[left=1in,right=1in,top=0.9in,bottom=0.9in]{geometry}
\usepackage{xcolor}


\usepackage[english]{babel}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{bibentry}

\usepackage{bbding,pifont} % two dingbat fonts


\usepackage{multicol}

\name{Soroush}{Bateni}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[5][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}\\
  \begin{tabular}{l@{}}
     {\itshape #4}
  \end{tabular}
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

\usepackage{ragged2e}
\usepackage{enumerate}



%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------

%\vspace*{-12mm}
\makecvtitle
\vspace*{-12mm}
%\nobibliography{main}
%\bibliographystyle{unsrt}
\begin{flushleft}
\faEnvelopeO\hspace{0.00em} soroush@berkeley.edu |
\hspace{0.25em}\faGlobe\hspace{0.00em}
\href{https://www.utdallas.edu/~soroush/}{utdallas.edu/$\sim$soroush} |
% \hspace{0.25em}\faLinkedinSquare\hspace{0.00em}
% \href{https://www.linkedin.com/in/sbateni}{linkedin.com/in/sbateni} |
\hspace{0.25em}\faGithub\hspace{0.00em} \href{https://github.com/Soroosh129}{github.com/Soroosh129} |
\hspace{0.25em}\faMobile\hspace{0.00em} (682) 330-5395
\end{flushleft}

\vspace{1mm}

\section{RESEARCH INTERESTS}
\textbf{Cyber-Physical Systems}, in particular, autonomous embedded systems such as self-driving vehicles.

\textbf{Real-Time Systems}, in particular, predictable embedded GPGPU computing and deterministic models of computation.



\section{EDUCATION}
{\customcventry{Graduated: May 2022}{PhD in Computer Science. GPA: 3.76.}{The
University of Texas at Dallas}{Richardson, TX}{}{}}
{\customcventry{Graduated: May 2018}{MS in Computer Science. Jonsson School
Graduate Scholarship. GPA: 3.72.}{The University of Texas at Dallas}{Richardson, TX}{}{}}
%{\customcventry{Graduated: July 2015}{BS in Software Engineering.}{Isfahan University of Technology}{Isfahan, Iran}{}{}}


\section{EXPERIENCE}


{\customcventry{May 2022 - Current}{Postdoc}{The University of California, Berkeley}{Berkeley, CA}{}
	{\begin{itemize}
    \item Research on
    \begin{itemize}
			\item deterministic heterogeneous distributed embedded systems in the
			context of \href{https://www.lf-lang.org}{Lingua Franca (LF)~\scalebox{0.75}{\faExternalLink}},
      \item pluggable schedulers for LF to create a viable
      platform for real-time systems research, and,
      \item enhancing the testability of autonomous embedded systems by
      enabling easy migration from Robot Operating System (ROS) to LF.
		\end{itemize}
    \item Leading undergraduate students on several projects, including the
    porting of Amazon's DeepRacer software stack from ROS to Lingua Franca.
      \item Supervisor: Prof. Edward A. Lee
		\end{itemize}
	}}

{\customcventry{May 2017 - May 2022}{Research Assistant}{The University of Texas at Dallas}{Richardson, TX}{}
{\begin{itemize}
  \item Published NeuOS, a timing-predictable DNN framework for autonomous embedded systems, designed to minimize energy consumption and maximize accuracy in USENIX ATC 2020.
  \item Published two papers in RTSS 2019 and RTAS 2020 about data constraints
  and memory management in autonomous embedded systems.
\end{itemize}
}}

{\customcventry{Fall 2020, Summer 2021}{Visiting Ph.D. Student Researcher}{The University of California, Berkeley}{Berkeley, CA}{}
	{\begin{itemize}
			\item Research on the semantics of Lingua Franca (\href{https://www.lf-lang.org}{lf-lang.org}), a synchronous programming language framework based on discrete time event models.
			\item Ported Autoware.Auto 1.0, an open-source autonomous driving
			framework to LF.
			\item Under the supervision of Prof. Edward A. Lee.
		\end{itemize}
	}}

{\customcventry{Summer 2019}{Research Intern}{Fujitsu Laboratories of America}{Richardson, TX}{}
	{\begin{itemize}
			\item Developed a comprehensive prototype of an efficient distributed collective intelligence system for edge-connected autonomous vehicles.
			\item Used Java, C++, and CUDA, along with open source ROS and Autoware software to implement an interactive computing framework using the latest NVIDIA embedded platforms. 
		\end{itemize}
	}}

{\customcventry{Spring 2015}{Stanford Crowd Research Collective}{Stanford University}{Remote}{}
	{\begin{itemize}
			\item Worked with a large research group on Daemo, under the supervision of Prof. Michael Bernstein.
		\end{itemize}
	}}


\section*{SELECTED PUBLICATIONS}
\bibliographystyle{unsrt}
\begin{enumerate}[\hspace{0.28in}]
  \setlength{\itemsep}{3pt}
  \setlength{\parskip}{0pt}
  \nobibliography{resume}%
  \item [2021] \bibentry{lee2021quantifying}
  \item [-] \bibentry{lohstroh2021toward}
  \item [2020] \bibentry{sor20202}
  \item [-] \bibentry{sor2020}
	\item [2019] \bibentry{sor2019}
	\item [2018] \bibentry{sor2018}
	\item [-] \bibentry{sor20182}
	\item [-] \bibentry{hush2018}
	\item [-] \bibentry{zheng20182}
	\item [-] \bibentry{hush20182}
	\item [2016] \bibentry{salimi2016}
\end{enumerate}


\section{LECTURES}
{\customcventry{Undergraduate Course - Summer 2018}{Sole Instructor}{Operating Systems Concepts}{UT Dallas}{}{}}
{\customcventry{Graduate Course - Spring 2018}{GPU/CUDA programming - Co-Instructor}{General Purpose GPU Computing}{UT Dallas}{}{}}
{\customcventry{Graduate Course}{GPU/CUDA programming - Co-Instructor}{Parallel Processing}{Isfahan University of Technology}{}{}}
{\customcventry{}{GPU/CUDA programming - Sole Instructor}{Medical Image and Signal Processing Research Center}{Isfahan University of Medical Sciences}{}{}}


\section{Skills}
{\customcventry{}{CUDA\_C, C, C++, C\#, Java, Python}{Programming Languages}{}{}{}}
{\customcventry{}{lflang/Lingua-Franca, NeuOS}{Open-Source Contributions}{}{}{}}
{\customcventry{}{Researched on GPU Drivers (NOUVEAU + GDev), embedded Linux, LITMUS \textsuperscript{RT} (Real-Time OS)}{Relevant System Experiences:}{}{}{}}
{\customcventry{}{ROS (Robot Operating System), Autoware, and Lingua Franca.}{Autonomous Vehicle and Embedded System Frameworks:}{}{}{}}
{\customcventry{}{Caffe (CaffeNet, AlexNet, ResNet, GoogleNet, VGGNet), Darknet (YOLO), TensorFlow}{Neural Network Frameworks}{}{}{}}
{\customcventry{}{NVIDIA Drive PX2 Autochauffeur, Jetson AGX Xavier, Jetson TX2, DGPU}{Platforms}{}{}{}}
{\customcventry{}{Proficient in English, love teamwork, and very passionate about research.}{Miscellaneous}{}{}{}}
%{\customcventry{}{English: Fluent. Persian: Native}{Languages}{}{}{}}
%\section{ADDITIONAL}
%\begin{minipage}{\maincolumnwidth}%
%	\small{
%    	\begin{itemize}
%          \item Relevant Coursework: Data Structures and Algorithms, Natural Language Processing, Computer Systems, Databases, Computer Security, Abstract Algebra
%          \item President of XYZ Club, Public Relations Manager of Swarthmore QWE Club
%          \item Programming Languages: Python, C, C++, PHP, Java, HTML/CSS, Javascript, jQuery, NodeJS
%          \item Fluent in Gibberish, conversational in Nonsense
%		\end{itemize}}%
%\end{minipage}%
%      
%}


\end{document}


%% end of file `template.tex'.
